---
title: "week_5_lab"
author: "Andrea Gracia"
date: "11/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(effsize)
library(broom)
library(ggbeeswarm)
library(car)
```

# Part 1: T-tests
Mass comparison between male & female chinstrap penguins

```{r}
#Exploring
chinstraps <- penguins %>% 
  filter(species=="Chinstrap")

#Basic plots, Histograms
ggplot(data=chinstraps, aes(x=body_mass_g)) +
  geom_histogram(bins=10)+
  facet_wrap(~sex)

#Basic plot, QQ Plot
ggplot(data=chinstraps, aes(sample=body_mass_g))+
  geom_qq()+
  facet_wrap(~sex)

#Descriptive stats
chinstraps %>% 
  group_by(sex) %>% 
  summarise(
    mean_mass=mean(body_mass_g),
    median_mass=median(body_mass_g),
    sd_mass=sd(body_mass_g),
    sample_size=n()
  )
```

Get vectors of body_mass_g for female and male chinstrap penguins separately

```{r}
chinstraps_f <- chinstraps %>% 
  filter(sex=="female") %>% 
  pull(body_mass_g)

chinstraps_m <- chinstraps %>% 
  filter(sex=="male") %>% 
  pull(body_mass_g)
```

## T-tests, a couple different ways 

1. Is there a significant difference in body mass between male and female chinstrap penguins?

```{r}
chinstrap_ttest <- t.test(chinstraps_f, chinstraps_m)
chinstrap_ttest

cohen.d(chinstraps_f, chinstraps_m)
```

Are male chinstrap penguin significantly larger(body mass) than female chinstrap penguins?
```{r}
t.test(chinstraps_m, chinstraps_f, alternative = "greater")

```























